---
title: "Creating Reporting Templates with Glue in R"
author: "LJ"
date: "2022-11-26"
output: html_document
---

## Introduction

In this notebook I will use `glue` to create templates as indicated in:
[Creating Reporting Templates with Glue in R.  DataScience+](https://datascienceplus.com/creating-reporting-template-with-glue-in-r/)

Written by: [Abdil Majed Raja](https://datascienceplus.com/author/abdulmajed-raja/)

## Using `glue`for reporting.

Automating reports can be done programatically using the `glue`R package.  This
package that interprets string literals in a fast and dependency-free way.  

In short, it helps concatenate data within strings that updates as data evolves.

Here, we'll see examples that will clarify the use of the package.

## Loading `glue` and dataset

```{r Installing glue}
pacman::p_load(glue,
               tidyverse,
               janitor)

```


```{r create copy of mtcars}
## Make a copy of mtcars, make a tibble and view it
mtcars_test <- mtcars %>% 
  rownames_to_column(var = "car") %>% 
  as_tibble()
  

mtcars_test %>% 
  head()

```

## First minimal reportng example

We'll work out a first example of a report that outputs basic information of the 
dataset we will be working with: mtcars

```{r create sample report that shows information about the dataset}
dset <- mtcars_test

about_dataset <- 'Dataset information: \n\n This dataset has {nrow(dset)} rows and {ncol(dset)} columns. \n There {ifelse(sum(is.na(dset)) == 1, "is", "are")} {sum(is.na(dset))} Missing Value(s).'

glue(about_dataset)

```


What `glue` is doing is taking the input string and showing the text with the info 
extracted directly from the data set in turn.  

With the same code we can extract information from any dataset we pass on to the 
variable dset.  For example, let's try with a dataset form the Ames Housing package.  
The raw dataset contains NAs that will be displayed.  

```{r sample report with a different dataset with NAs}
dset <- AmesHousing::ames_raw

about_dataset <- 'Dataset information: \n\n This dataset has {nrow(dset)} rows and {ncol(dset)} columns. \n There {ifelse(sum(is.na(dset)) == 1, "is", "are")} {sum(is.na(dset))} Missing Value(s).'

glue(about_dataset)

```


## Second example report content of the dataset

We will write a sentence for the data of each row.

```{r}
mtcars_test %>% 
  dplyr::slice_sample(n = 6) %>% 
  glue_data("{car} has {cyl} cylinders and {hp} hp")
  

```
`glue_data` iterates all the rows to bring the concatenation.  Using `glue()` only 
would have thrown an error since it can only take one vector or string. 

## Back to Home

[Home](index.html)








